---
title: "Programming challenge 2"
output: 
  learnr::tutorial:
     progressive: true
     allow_skip: true
highlight: textmate
runtime: shiny_prerendered
---

```{r setup, include=FALSE}

library(learnr)
library(tidyverse)
library(timetk)
library(lubridate)
library(ggTimeSeries)
library(modeltime)
library(tidymodels)
library(learnrhash)

m5_calendar <- read_csv("calendar.csv")

m5_price <- read_csv("m5_pricetrim.csv")

m5_sales <- read_csv("m5_salestrim.csv")

key_list <- m5_sales%>%
  distinct(id)

missing_example <- read_csv("missing example.csv")%>%
  mutate(date = mdy(date))

adding_missing_dates <- missing_example%>%
     pad_by_time(.date_var = date)

m5_data <- m5_sales%>%
  pivot_longer(cols = -c(1:6), names_to = "d", values_to = "sales")%>%
  left_join(m5_calendar, by = "d")%>%
  select(1:10,12)

split <- m5_data%>%
  filter(id %in% c("FOODS_1_004_CA_3_evaluation","HOBBIES_1_007_CA_1_evaluation"))%>%
  filter_by_time(.date_var = date, .start_date = "2014")%>%
  select(id,date,sales,wday)%>%
  timetk::time_series_split(date_var = date, assess = "3 months", cumulative = TRUE)
  

m5_data_v1_calendar <- m5_sales%>%
  pivot_longer(cols = -c(1:6), names_to = "d", values_to = "sales")%>%
  left_join(m5_calendar, by = "d")

knitr::opts_chunk$set(echo = FALSE)
```


## Exercise

### Notes 

1. You have to complete the coding for the 10 task given. 

2. you have to replace `---` with appropriate code.

3. Once you complete, click the `Run code` button.

4. Once you answered all the questions, go to submit section and do the following

|  a. Go to Submit section
|  b. click `Generate` button
|  c. once the hash code generated , select using `select hash` button
|  d. then copy the hash code by clicking `copy hash to clipboard`button
|  e. open the google form link and fill the details and submit


### Exercise 1

`m5_data` available for you. complete the code with appropriate function to select first 6 rows of the data

```{r e1, exercise = TRUE}

---(m5_data)

```

### Exercise 2

complete the code to identify the no of unique departments in the `m5_data`

```{r e2, exercise = TRUE}

m5_data%>%
  ---(---)

```

### Exercise 3

From the `m5_data` 1) filter `FOODS_1_011_CA_3_evaluation` using the `id` column 2) aggregate the daily sales to `monthly` sales and 3) plot the time series by specifying appropriate arguments

```{r e3, exercise = TRUE}

m5_data%>%
  ---(---)%>%
  ---(---)%>%
  ---(.date_var = ---, .value = --- )

```

### Exercise 4

From the `m5_data` 1) filter `HOBBIES_1_001_CA_1_evaluation` using the `id`column 2) filter the time series starting from `2015 January` till `2016 Mar 31` and 3) plot the time series

```{r e4, exercise = TRUE}

m5_data%>%
  ---(---)%>%
  ---(---)%>%
  ---(.date_var = ---, .value = --- )

```

### Exercise 5

An example with missing values is available for you as `missing_example`. add the missing dates and store it in the `adding_missing_dates` variable. 

```{r e5, exercise = TRUE}

adding_missing_dates <- ---%>%
  ---(---)

```


### Exercise 6 

with the `adding_missing_dates` in the previous exercise , create a dataframe to fill the missing values using `na_interpolation` method with the option as `spline` and store them in the variable `replaced_value`

```{r e6, exercise = TRUE}

replaced_value <- ---(repalced_value = ---)
  

```


### Exercise 7

m5_data with calendar info added available as `m5_data_withcalendar`. generate the calendar events for the snap days in california. 


```{r e7, exercise = TRUE}

m5_data_withcalendar%>%
  filter(id == "FOODS_1_001_CA_1_evaluation")%>%
  filter_by_time(.date_var = date, .start_date = "2011-01","2015")%>%
  ---(--- = ---,  --- = ---)+
  xlab(NULL)+
  ylab(NULL)+
  theme(strip.background = element_blank(),
        panel.grid = element_blank(),
        legend.position = 'bottom')+
  facet_wrap(~Year, ncol = 1)

``` 

### Exercise 8

with the `m5_data`, add the variables for lag 3 and 12 of sales.


```{r e8, exercise = TRUE}

m5_data%>%
  filter(id == "FOODS_1_004_CA_3_evaluation")%>%
  filter_by_time(.date_var = date, .start_date = "2013")%>%
  ---(--- = ---, --- = --- )

```

### Exercise 9

with the `m5_data` add the time related variables

```{r e9, exercise = TRUE}

m5_data%>%
  filter(id == "HOBBIES_1_005_CA_1_evaluation")%>%
  ---(--- = ---)

```


### Exercise 10


Split the data in to training and test by defining 2 months for test and the rest for train

```{r e10, exercise = TRUE}

m5_data%>%
  filter(id %in% c("FOODS_1_004_CA_3_evaluation","HOBBIES_1_007_CA_1_evaluation"))%>%
  filter_by_time(.date_var = date, .start_date = "2014")%>%
  ---(date_var = date, --- = --- , --- = ---)

```

### Exercise 11

apply `arima_reg()` model to train the data. The `split`data which contains both train and test values available for you. 

```{r e11, exercise = TRUE}

model_fit <- --- %>%
  ---(engine = ---)%>%
  ---(--- , ---)

```

## Submit




```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(ui_before = default_ui(url = "https://forms.gle/Xmqe5reyAUdGJnH18")
)
```